Generate data for NOBA cod ensemble modeling

### 2020-05-27 NOBAcod.Rmd
load_nc_annage works for fisheries but only one fleet per species right now

```{r load_fisheries}

@@

source(here("R/load_nc_annage.R"))
source(here("R/load_fisheries.R"))

@@

@@

fishcatchage

@@

Do we want catch by fishery? Yes. No fishery column here, check what it is doing.
fishdiscage is empty, make sure there is no discard output from NOBA for these species.

@@

NOBA has multiple fleets for cod, so add fleet column to output.

@@

>>>>

```{r load_fisheries, eval=FALSE}

@@

# source(here("R/load_nc_annage.R"))
# source(here("R/load_fisheries.R"))

@@

#for testing line by line
bboxes <- boxes
dir <- d.name
select_variable <- "Catch"

@@

fishcatchage[1:100,]

@@

Do we want catch by fishery? Yes. No fishery column here, check what it is doing.
fishdiscage is empty, make sure there is no discard output from NOBA for these species (confirmed).

@@

NOBA has multiple fleets for cod (but they are not in output!), so add fleet column to output.

@@

Plot catch at age; aggregate over polygons, apply sample_fish:

```{r catchannage}

  #numbers based fishery independent survey for age and length comps
  # same user specifications as indices
  #fishery catch at age each observed timestep summed over observed polygons
  # catch at age by area and timestep
  catch_numbers <-  atlantisom::create_fishery_subset(dat = fishcatchage,
                                                      time = fishtime,
                                                      species = select_groups,
                                                      boxes = fishboxes)

  # if we want replicates for obs error this sample function will generate them
  catch_age_comp <- list()
  for(i in 1:n_reps){
    catch_age_comp[[i]] <- atlantisom::sample_fish(catch_numbers, fisheffN)
  }

  # save fishery age comps
  #if(save){
    saveRDS(catch_age_comp, file.path(d.name, paste0(scenario.name, "fishObsFullAgeComp.rds")))
  #}

NOTE that the fleet column is lost in the `atlantiom::sample_fish` function!

Look at only every 10 years output (this is a sample, effN = 1000 for the year, which is 200 per timestep here; see calc below confirming):

```{r plotfullcatchage}

#read in comp data
# age_comp_data <- readRDS(file.path(d.name, paste0(scenario.name, "survObsFullAgeComp.rds")))
# age_comp_data <- age_comp_data[[1]]

fish_age_comp <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsFullAgeComp.rds")))
fish_age_comp <- fish_age_comp[[1]]

#add this to om_indices function so that this has years when read in
fish_age_comp$time <- fish_age_comp$time/fstepperyr

Catage <- filter(fish_age_comp, time %in% c(30.0, 40.0, 50.0, 60.0, 70.0, 79.8))

Catageplot <- ggplot(Catage, aes(x=agecl, y=atoutput)) +
    geom_point() +
    theme_tufte() +
    labs(subtitle = paste(scenario.name,
                          Catage$species))

  Catageplot + facet_wrap(~time, ncol=3, scales="free_y")

```{r testeffn}

fish_age_comp %>%
  filter(time<31) %>%
  summarise(sum(atoutput))

Appears to be working for single fleet per species now.
